Measuring the Type Ia supernova delay time distribution via host galaxy rates in the Dark Energy Survey

### 2021-01-29 draft.tex
Updates from Overleaf

It is also possible to estimate the SFH of an individual galaxy through the modelling of its stellar populations via spectral energy distribution (SED) fitting. Works such as \citet{Maoz2011}, \citet{Maoz2012} and \citet{Graur2013} estimated the DTD by measuring SFHs for a sample of field galaxies and comparing them to the number of SNe detected in each galaxy (the SFHR method), and have led to results that suggest a DTD power law with $\beta$ consistent with $-1$ \citep[e.g.][]{Maoz2011,Graur2013}. \citet{Childress2014} showed that the $A+B$ parameterisation arises as a direct consequence of the combination of a power-law DTD with the SFHs of galaxies. The recent advances of integral field spectroscopy (IFS) allows for an extension of the SFHR method, by reconstructing the SFH for hundreds or thousands of local regions of each SN Ia host galaxy. Using this method, \citet{Castrillo2020} find a power-law slope of $-1.1\pm0.3$, while \citet{Shen2021} find $-1.4\pm0.3$.

@@

\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{figs/SN_efficiencies.png}
    \caption{SN detection efficiencies split up by DES field. The $y-$axis represents the fraction of simulated SNe in a given redshift bin that would have been detected by DES-SN and passed light curve quality cuts.
    \label{fig:SN_efficiency}}
\end{figure}

@@

The numbers of SN hosts and field galaxies passing these cuts are listed in Table \ref{tab:cuts}. The final samples comprise 1204 SN host galaxies and 48,177 field galaxies.

@@

The results of our SED fitting are shown in Fig. \ref{fig:mass_hist_hosts_field}. The upper panel, with both the SN hosts and field galaxies displayed, shows the vastly different distributions of the two samples. SN hosts are preferentially high mass galaxies, whereas the field galaxy distributions increases down to lower masses, peaking around $10^{8.5}~\mathrm{M}_{\odot}$. In the bottom panel, the same field galaxy stellar mass distribution is shown on a log scale, along with the stellar mass functions (SMFs) from the ZFOURGE survey \citep{Tomczak2014} that best represent the redshift range of the DES field galaxies. Above $10^{8.5}~\mathrm{M}_{\odot}$, the DES field galaxy distribution closely follows the ZFOURGE SMFs, particularly that from $0.5<z<0.75$, indicating that the DES sample is representative of field galaxies in this redshift range.%To estimate uncertainties on the physical properties, we resample the photometry from a Gaussian distribution formed by the flux measurements and their uncertainties and rerun the SED fit. This procedure is repeated 1000 times. 
%%%% INCOMPLETENESS %%%%

@@

To correct for incompleteness caused by the magnitude limited nature of the survey we follow the prescription of e.g. \citet{Sullivan2006, Smith2012} by using a $V_{\mathrm{max}}$ method of \citet{Schmidt1968}. For each galaxy in the sample we calculate the maximum volume within which it would have been observed given its absolute magnitude and $k-$correction. A correction of $V_{\mathrm{survey}}/V_{\mathrm{max}}$ is applied to all galaxies for which $V_{\mathrm{max}} < V_{\mathrm{survey}}$, where $V_{\mathrm{survey}}$ is the maximum volume reached by the survey. In our case this corresponds to the volume at $z=0.8$. Fig \ref{fig:vmax_field} shows the distribution of the correction among galaxies in the sample. The vast majority of galaxies require no correction, meaning they would have been observed beyond the maximum volume considered. Roughly 1\% of objects have a correction greater than 1, with the distribution well described by a power-law function.

>>>>

It is also possible to estimate the SFH of an individual galaxy through the modelling of its stellar populations via spectral energy distribution (SED) fitting. Works such as \citet{Maoz2011}, \citet{Maoz2012} and \citet{Graur2013} estimated the DTD by measuring SFHs for a sample of field galaxies and comparing them to the number of SNe detected in each galaxy (the SFHR method), and have led to results that suggest a DTD power law with $\beta$ consistent with $-1$ \citep[e.g.][]{Maoz2011,Graur2013}. \citet{Childress2014} showed that the $A+B$ parameterisation arises as a direct consequence of the combination of a power-law DTD with the SFHs of galaxies. The recent advances of integral field spectroscopy (IFS) allows for an extension of the SFHR method, by reconstructing the SFH for hundreds or thousands of local regions of each SN Ia host galaxy. Using this method, \citet{Castrillo2020} find a power-law slope of $-1.1\pm0.3$, while \citet{Chen2021} find $-1.4\pm0.3$.

@@

\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{figs/SN_efficiencies.png}
    \caption{SN detection efficiencies split up by DES field. The $y-$axis represents the fraction of simulated SNe in a given redshift bin that would have been detected by DES-SN and passed light curve quality cuts. The curves are capped at efficiencies around 0.5 because DES is restricted to $\sim6$ month observing seasons each calendar year.
    \label{fig:SN_efficiency}}
\end{figure}

@@

The numbers of SN hosts and field galaxies passing these cuts are listed in Table \ref{tab:cuts}. The final samples comprise 1204 SN host galaxies and 48,177 field galaxies. The volume-weighted mean redshifts are 0.65 and 0.63 for SNe and field galaxies, respectively.

@@

The results of our SED fitting are shown in Fig. \ref{fig:mass_hist_hosts_field}. The upper panel, with both the SN hosts and field galaxies displayed, shows the vastly different distributions of the two samples. SN hosts are preferentially high mass galaxies, whereas the field galaxy distributions increases down to lower masses, peaking around $10^{8.5}~\mathrm{M}_{\odot}$. In the bottom panel, the same field galaxy stellar mass distribution is shown on a log scale, along with the stellar mass function (SMF) from the ZFOURGE survey \citep{Tomczak2014} that best represents the redshift range of the DES field galaxies. Above $10^{8.5}~\mathrm{M}_{\odot}$, the DES field galaxy distribution closely follows the ZFOURGE SMF for $0.5<z<0.75$, indicating that the DES sample is representative of field galaxies in this redshift range.%To estimate uncertainties on the physical properties, we resample the photometry from a Gaussian distribution formed by the flux measurements and their uncertainties and rerun the SED fit. This procedure is repeated 1000 times. 
%%%% INCOMPLETENESS %%%%

@@

To correct for incompleteness caused by the magnitude limited nature of the survey we follow the prescription of e.g. \citet{Sullivan2006, Smith2012} by using a $V_{\mathrm{max}}$ method based on \citet{Schmidt1968}. For each galaxy in the sample we calculate the maximum volume within which it would have been observed given its absolute magnitude and $k-$correction. A correction of $V_{\mathrm{survey}}/V_{\mathrm{max}}$ is applied to all galaxies for which $V_{\mathrm{max}} < V_{\mathrm{survey}}$, where $V_{\mathrm{survey}}$ is the maximum volume reached by the survey. In our case this corresponds to the volume at $z=0.8$. Fig \ref{fig:vmax_field} shows the distribution of the correction among galaxies in the sample. The vast majority of galaxies require no correction, meaning they would have been observed beyond the maximum volume considered. Roughly 1\% of objects have a correction greater than 1, with the distribution well described by a power-law function.
